Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-20 minimax.tex
very minor

Given $\pprofile$ and $\pw$ (that represent the current knowledge about agent preferences and the PSR),
the maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$. %where $\pprofile$ and $\pw$ represent our knowledge so far.
We formalize the notion of minimax regret in multiple steps.
First of all, $\Regret(x, \profile, \w)$
is the “regret” of selecting $x$ as a winner instead of the optimal alternative under $\profile$ and $\w$:
$$\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).$$
 The {\em pairwise maximum regret} of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
$$\PMR(x,y;\pprofile,W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).$$
The maximum regret %$\MaxR(x;\pprofile,W)$ 
is the worst-case loss of $x$:
\begin{align}
\MaxR(x;\pprofile,W) & = \max_{y \in A} \PMR(x,y; \pprofile, W) \\ &= \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
\end{align}
$\MaxR(x;\pprofile,W)$ is the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that jointly maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
Finally,  $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending a minimax optimal alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
Picking as consensus choice an alternative associated with minimax regret provides a recommendation that gives worst-case guarantees. 
In cases of ties, %in minimax regret, 
we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.

>>>>

Given $\pprofile$ and $\pw$ (that represent the current knowledge about agent preferences and the PSR),
the maximum regret is considered by assuming that an adversary can both 1) extend the partial profile $\pprofile$ into a complete profile, and 2) instantiate the weights choosing among any weight vector in $\pw$. %where $\pprofile$ and $\pw$ represent our knowledge so far.
We formalize the notion of minimax regret in multiple steps.
First of all, $\Regret(x, \profile, \w)$
is the “regret” of selecting $x$ as a winner instead of the optimal alternative under $\profile$ and $\w$:
$$\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).$$
 The {\em pairwise maximum regret} of $x$ relative to $y$ given the partial profile $\pprofile$ and the set of weights $W$ is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
$$\PMR(x,y;\pprofile,W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).$$
The maximum regret %$\MaxR(x;\pprofile,W)$ 
is the worst-case loss of $x$:
\begin{align}
\MaxR(x;\pprofile,W) & = \max_{y \in A} \PMR(x,y; \pprofile, W) \\ &= \max_{\w \in W} \max_{\profile \in C(\profile)} \Regret(x; \profile, \w).
\end{align}
$\MaxR(x;\pprofile,W)$ is the result of an adversarial selection of the complete profile $\profile \in C(\pprofile)$ and of the scoring vector $\w \in W$ that jointly maximize the loss between $x$ and the true winner under $\profile$ and $\w$.
Finally,  $\MMR(\pprofile,W) = \min_{x \in A} \MaxR(x;\pprofile,W)$ is the value of {\em minimax regret} under $\pprofile$ and $W$, obtained when recommending a {\em minimax optimal} alternative $x^*_{\pprofile, W} \in A^*_{\pprofile, W} = \argmin_{x \in A} \MaxR(x;\pprofile,W)$.
Picking as consensus choice an alternative associated with minimax regret provides a recommendation that gives worst-case guarantees. 
In cases of ties, %in minimax regret, 
we can return all minimax alternatives $A^*_{\pprofile, W}$ as winners or pick one of them using some tie-breaking strategy.
